IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/abstract.tex
Revert "jcmnew intro"
This reverts commit 0888d98c8975a3bc3aaef3250801c285cfadedd4.

\begin{abstract}
    Many important security problems in JavaScript, such as browser extension
    security, untrusted JavaScript libraries and
    safe integration of mutually distrustful websites (mash-ups), may be effectively addressed using an efficient implementation
    of information flow control.
We present a coarse-grained IFC system that
can be implemented  non-intrusively, resulting in
much greater implementation efficiency than previous finer-grained approaches.
The central concept is an isolation mechanism whose operation does not
depend too much on the details of the programming language used.
We thus present a \emph{general} method for adding IFC to existing
languages that is largely \emph{indifferent} to the choice of language.
Additionally, we describe how to relate optimized concrete implementations
to the IFC systems produced by our technique and show how various
proposed and existing IFC systems conform to our formal framework
and therefore enjoy the semantic properties we prove.
\end{abstract}

>>>>

\begin{abstract}
    Many important security problems in JavaScript, such as browser extension
    security, untrusted JavaScript libraries and
    safe integration of mutually distrustful websites (mash-ups), may be effectively addressed using an efficient implementation
    of information flow control.
We formally specify a coarse-grained IFC system that
can be implemented  non-intrusively, resulting in
much greater implementation efficiency than previous finer-grained approaches.
The central concept is an isolation mechanism whose operation does not
depend too much on the details of the programming language used.
Thus, we have a \emph{general} method for adding IFC to existing
languages that is largely \emph{indifferent} to the choice of language.
Additionally, we describe how to relate optimized concrete implementations
to the IFC systems produced by our technique and show how various
proposed and existing IFC systems conform to our formal framework
and therefore enjoy the semantic properties we prove.
\end{abstract}

### 2014-07-08 paper/intro.tex
Revert "jcmnew intro"
This reverts commit 0888d98c8975a3bc3aaef3250801c285cfadedd4.

\section{Introduction}
\label{sec:intro}

@@

Our contributions can be summarized as follows:
\begin{itemize}
  \item We give formal semantics for a core coarse-grained
  information flow control language.
  We then show how a large class of target languages can be combined
  with this IFC language and prove that the result provides
  non-interference. (Section~\ref{sec:retrofit})
%  \item We show how to extend the Matthews-Findler method from just
%  languages that are not simply expressions evaluating to values,
%  but may be collections of threads executing nondeterministically.
  \item We provide a proof technique to show the non-interference
  of a concrete semantics for a potentially optimized IFC language
  by means of an isomorphism, and show a class of restrictions on
  the IFC language that preserves non-interference. (Section~\ref{sec:formal})
  \item We connect our formal semantics to real implementations of
  coarse-grained IFC systems for JavaScript and Haskell, and explain
  how our system could be used to enforce IFC in C. (Section~\ref{sec:real})
  \item We briefly describe ways to enrich the core IFC language with
  more advanced concepts such as labeled values, privileges, or a
  notion of clearance. (Section~\ref{sec:extensions})
  \item We informally relate our results to a monadic interpretation
      of IFC which guided our design. (Section~\ref{sec:monad})     
\end{itemize}

>>>>

\section{Introduction}
\label{sec:intro}
\Red{DM had some very good comments on how to make this sound less
  like a pitch for LIO. Outline for something more compelling (not
  necessarily in this order):
\begin{itemize}
  \item Motivate IFC
  \item Coarse grained IFC is easy
  \item Coarse grained IFC is sufficient (vs. fine grained); do by citation
  \item We have the right API and it's language-agnostic; proof is also language independent
  \item You can ``drop it in''
\end{itemize}
}

@@

Our contributions can be summarized as follows:
\begin{itemize}
  \item We give formal semantics for a core coarse-grained
  information flow control language.
  We then show how a large class of target languages can be combined
  with this IFC language and prove that the result provides
  non-interference. (Section~\ref{sec:retrofit})
%  \item We show how to extend the Matthews-Findler method from just
%  languages that are not simply expressions evaluating to values,
%  but may be collections of threads executing nondeterministically.
  \item We provide a proof technique to show the non-interference
  of a concrete semantics for a potentially optimized IFC language
  by means of an isomorphism, and show a class of restrictions on
  the IFC language that preserves non-interference. (Section~\ref{sec:formal})
  \item We connect our formal semantics to real implementations of
  coarse-grained IFC systems for JavaScript and Haskell, and explain
  how our system could be used to enforce IFC in C. (Section~\ref{sec:real})
  \item We briefly describe ways to enrich the core IFC language with
  more advanced concepts such as labeled values, privileges, or a
  notion of clearance. (Section~\ref{sec:extensions})
\end{itemize}
